Geographically aware estimates of remotely sensed water properties for Chesapeake Bay

### 2022-10-05 manuscript/manuscript.tex
prep pdf ms

@@

Our tuned RF models for salinity, turbidity, and temperature had a root mean square error (RMSE) of 2.34 ($R^2$=0.91), 32.2 ($R^2$=0.07), and 1.8 ($R^2$=0.96) respectively (Table 1, Figure 2). Out-of-sample validation performance was excellent for salinity and temperature models but poor for the turbidity model (Figure 2, Figure S1). Despite excellent overall performance for the temperature and salinity models, there was some indication of poor performance at the extremes. The models were unable to recover very low temperature values ($<$ 0 C) or very high temperature and salinity values ($>$ 30 C, $>$ 23 salinity, Figure 2). One explanation for these areas of poor performance is that such extremes were rare in the observational dataset (Table S2). The salinity model however did faithfully capture areas of low salinity (Figure 2). These low salinity values can be regarded as low uncertainty (high confidence) estimates given the extent to which the upper tributaries are well represented in the observational dataset (Figure S2).

>>>>

\begin{figure}[ht!]
    \begin{center}
          \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/data-processing_model-architecture}
          \caption{Diagram of data processing, model fitting, tuning, and prediction pipeline.}
    \end{center}    
\end{figure}

@@

Our tuned RF models for salinity, turbidity, and temperature had a root mean square error (RMSE) of 2.34 ($R^2$=0.91), 32.2 ($R^2$=0.07), and 1.8 ($R^2$=0.96) respectively (Table 1, Figure 2). Out-of-sample validation performance was good for salinity and temperature models but poor for the turbidity model (Figure 2, Figure S1). Despite excellent overall performance for the temperature and salinity models, there was some indication of poor performance at the extremes. The models were unable to recover very low temperature values ($<$ 0 C) or very high temperature and salinity values ($>$ 30 C, $>$ 23 salinity, Figure 2). One explanation for these areas of poor performance is that such extremes were rare in the observational dataset (Table S2). The salinity model however did faithfully capture areas of low salinity (Figure 2, S3). These low salinity values can be regarded as low uncertainty (high confidence) estimates given the extent to which the upper tributaries are well represented in the observational dataset (Figure S2).
